Movie Night Voting Tabulation
=============================

## Setup

<details><summary>Click here for setup code</summary>

```{r, message = FALSE, warning = FALSE}
setwd('~/Personal/MovieNight')
library(tidyverse)
library(pheatmap)
devtools::load_all('~/MyProjects/AfterSl1p/')
theme_set(theme_bw())

cols = c('#878787','#FDDBC7','#B2182B')
ranklevs = c('I would NOT come to watch this film',
		  'I do not love this film but would still show up',
		  'I would REALLY LIKE to watch this film')
make_rank = function(x){
	x = factor(x, levels = ranklevs)
	x = as.numeric(x) -2
	return(x)
}
```

</details>

## Import and Clean Data

The voting data are available as a .csv file [here](./data/current_week.csv).

<details><summary>Click here for data wrangling code</summary>

```{r}
dat = read.csv('data/current_week.csv', stringsAsFactors = FALSE, header = FALSE)
datm = as.matrix(dat[,-1])

tdf = read.csv('data/current_movies.csv', row.names = 1, header = FALSE, 
			   stringsAsFactors = FALSE)
titles = tdf[[1]]
names(titles) = rownames(tdf)

datm[datm %in% names(titles)] = titles[datm[datm %in% names(titles)]]

colnames(datm) = datm[1,]
datm = datm[-1,]
```

</details>


## Tabulate the results

```{r,  warning = FALSE, results = 'hold'}
dat_num = (datm
		   %>% data.frame()
		   %>% mutate_all(make_rank))
results = sort(colSums(dat_num), decreasing = TRUE)
res_df = data.frame(results)
res_df
print('The winner is:')
print(names(results)[1])
```

## Pics or it didn't happen

```{r, fig.width = 9, warning = FALSE}
brk_levs = c('I would NOT come\nto watch this film',
			 'I do not love this film\nbut would still show up',
			 'I would REALLY LIKE\nto watch this film')
dat_long = (datm
			%>% data.frame()
			%>% gather(Movies, Votes)
			%>% mutate(Votes = factor(Votes, levels = ranklevs,
									  labels = brk_levs),
					   Movies = factor(Movies, levels = names(results))))
plt = ggplot(dat_long, aes(x = Movies, fill = Votes)) +
	geom_histogram(stat = 'count') +
	scale_fill_manual(values = cols, name = 'Vote Value') +
	ylab('Vote Count') +
	rotate_ticks() +
	theme(legend.text = element_text(margin = margin(t = 0.5,
													 b = 0.5,
													 unit = 'lines')))
plt

png(filename = 'current_week.png', height = 480, width = 800)
plt +
	theme(axis.title = element_text(size = 20),
		  axis.text.y = element_text(size = 15),
		  axis.text.x = element_text(size = 15,
		  						  angle = 90,
		  						  hjust = 1,
		  						  vjust = 0.5),
		  legend.text = element_text(size = 15, margin = margin(t = 0.5,
		  													  b = 0.5,
		  													  unit = 'lines')),
		  legend.title = element_text(size = 20))
		  #legend.key = element_rect(colour = 'white', size = 10))
dev.off()
```

## Executive Summaries Go At the Bottom

* The survey was completed 11 times, and all movies were ranked each time.
* Romy and Michele's High School Reunion is the winner with 8 positive votes and
0 negative votes.
* There were three movies that garnered negative votes: Tremors and Twister with 
one down-vote each, and Babe 2 with two.
* Beetlejuice got the fewest positive votes (1), but it tied with Twister in the
scoring because of Twister's single negative vote.
